Too hard to get: the role of probabilistic expectations and cognitive complexity in destructive multi-dimensional reference points

### 2025-02-25 manuscript-apa.qmd
update yaml and structure of manuscript

---
title: "Too hard to get: the role of probabilistic expectations and cognitive complexity in destructive multi-dimensional reference points"
shorttitle: "Destructive multi-dimensional reference points"

author:
  - name: Aspen Han
    corresponding: true
    orcid: 0000-0003-1474-7968
    email: xiangyuhan@uchicago.edu
    affiliations:
      - name: University of Chicago
        department: Department of Economics, Division of Social Sciences
        address:  1126 E. 59th Street
        city: Chicago
        region: IL
        postal-code: 60637

author-note:
  disclosures:
    study-registration: null
    data-sharing: null
    related-report: null
    conflict-of-interest: null
    financial-support: null
    authorship-agreements: null
    gratitude: null

abstract: "This is the abstract. Lorem ipsum lorem ipsum lorem ipsum lorem ipsum lorem ipsum lorem ipsum lorem ipsum lorem ipsum lorem ipsum lorem ipsum lorem ipsum lorem ipsum lorem ipsum lorem ipsum lorem ipsum lorem ipsum lorem ipsum lorem ipsum lorem ipsum lorem ipsum lorem ipsum lorem ipsum"

keywords: [reference points, multi-dimensional, conflicting]

bibliography: bibliography.bib

floatsintext: true

editor_options: 
  chunk_output_type: console

knitr:
  opts_chunk:
    out.width: "75%"

format:
  apaquarto-pdf:
    documentmode: man
    keep-tex: true
    list-of-figures: true
    fig-width: 6
    fig-asp: 0.618
    fig-align: center
    include-in-header:
      text: |
      #remove extra space between main list and sublist
        \usepackage{enumitem}
        \setlist[itemize]{topsep=0pt,itemsep=0pt,partopsep=0pt,parsep=0pt}
        \setlist[enumerate]{topsep=0pt,itemsep=0pt,partopsep=0pt,parsep=0pt}

---

>>>>

---
title: "Too hard to get: the role of probabilistic expectations and cognitive complexity in destructive multi-dimensional reference points"
shorttitle: "Destructive multi-dimensional reference points"
author:
  - name: Aspen Han
    corresponding: true
    orcid: 0000-0003-1474-7968
    email: xiangyuhan@uchicago.edu
    affiliations:
      - name: University of Chicago
        department: Department of Economics, Division of Social Sciences
        address:  1126 E. 59th Street
        city: Chicago
        region: IL
        postal-code: 60637
author-note:
  disclosures:

    study-registration: null
    data-sharing: null
    related-report: null
    conflict-of-interest: null
    financial-support: null
    authorship-agreements: null
    gratitude: null
abstract: "This is the abstract. Lorem ipsum lorem ipsum lorem ipsum lorem ipsum lorem ipsum lorem ipsum lorem ipsum lorem ipsum lorem ipsum lorem ipsum lorem ipsum lorem ipsum lorem ipsum lorem ipsum lorem ipsum lorem ipsum lorem ipsum lorem ipsum lorem ipsum lorem ipsum lorem ipsum lorem ipsum"
keywords: [reference points, multi-dimensional, conflicting]
bibliography: bibliography.bib
floatsintext: true
editor_options: 
  chunk_output_type: console
knitr:
  opts_chunk:

    out.width: "75%"
format:

  apaquarto-pdf:
    documentmode: man
    keep-tex: true
    list-of-figures: true
    fig-width: 6
    fig-asp: 0.618
    fig-align: center
    include-in-header:
      #remove extra space between main list and sublist
      text: |
        \usepackage{enumitem}
        \setlist[itemize]{topsep=0pt,itemsep=0pt,partopsep=0pt,parsep=0pt}
        \setlist[enumerate]{topsep=0pt,itemsep=0pt,partopsep=0pt,parsep=0pt}
---
